Issues with Dynamical Measurements Across the Disk

### 2019-03-07 paper/ms.tex
Small edits

From Figure \ref{fig:range_deltaphi} it is clear that the range of midplane
values spanned in a given $\Delta \phi$ quickly saturates at $\Delta \phi
\gtrsim \pi/2$ radians (i.e. one quarter of the way around the Galactic disk
from the Sun). At far smaller $\Delta \phi$ it reaches the level of deviation
required for an $\mathcal{O}(1)$ systematic error in $J_z$ for our fiducial
thin-disk-like orbit (\thincolor horizontal line in Figure
\ref{fig:range_deltaphi}). For the three simulations considered, the median
range exceeds this value at $\Delta \phi/\pi > 0.036, 0.047,
0.10\,\text{rad}$, with corresponding physical scales of $\lambda \sim 465,
610, 1290\,\pc$ for m12i, m12f, and m12m, respectively. These can be
considered estimates of the range of validity for an extension of the locally
determined axisymmetric coordinate system, at least when it comes to the study
of stars on quasi-circular orbits.

>>>>

From Figure \ref{fig:range_deltaphi} it is clear that the range of midplane
values spanned in a given $\Delta \phi$ quickly saturates at $\Delta \phi
\gtrsim \pi/2$ radians (i.e. one quarter of the way around the Galactic disk
from the Sun). At far smaller $\Delta \phi$ it reaches the level of deviation
required for an $\mathcal{O}(1)$ systematic error in $J_z$ for our fiducial
thin-disk-like orbit (\thincolor{} horizontal line in Figure
\ref{fig:range_deltaphi}). For the three simulations considered, the median
range exceeds this value at $\Delta \phi/\pi > 0.036, 0.047,
0.10\,\text{rad}$, with corresponding physical scales of $\lambda \sim 465,
610, 1290\,\pc$ for \mi{}, \mf{}, and \mm{}, respectively. These can be
considered estimates of the range of validity for an extension of the locally
determined axisymmetric coordinate system, at least when it comes to the study
of stars on quasi-circular orbits.
